FEM Model Analysis

### 2021-01-10 FEM_R/model_analysis.Rmd
Added survival curve to debug document

>>>>

### Survival Curve

```{r echo = FALSE}
cohort <- read_dta('ELSA_cohort/ELSA_cohort_summary.dta')

cohort$age <- (cohort$year - 2012) + 50

cohort$survival <- cohort$m_endpop_all / cohort$m_endpop_all[1]
cohort$survival_m <- cohort$m_endpop_m / cohort$m_endpop_m[1]
cohort$survival_f <- cohort$m_endpop_f / cohort$m_endpop_f[1]

# plot up survival curve
ggplot(cohort, aes(x=age, y=survival)) +
        geom_line(col='black', size=0.3) +
        labs(title='Cohort Survival: All', y='Survival', x='Age')
```
